Iterative construction of replicated designs based on Sobol' sequences

### 2016-06-30 crass/crassnew.tex
Last typos in crassnew.tex

\begin{e-definition}%[Replicated designs]
\label{rep.designs}
Consider $\vx \in [0,1)^s$, and $\vx_u \in [0,1)^{s-|u|}$ the subset of elements of $\vx$ given by $u\subsetneq \{1,\dots,s\}$, where $|u|$ is the cardinality of $u$. Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in $[0,1)^{s}$, and denote by $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp. $\mathcal{P}'^u$) the subset of elements of points in $\mathcal{P}$ (resp. $\mathcal{P}'$) indexed by $u$. We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a=1,\dots,s-1$, if for any $u\subsetneq \{1,\dots,s\}$ with $|u|=a$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ are the same point set in $[0,1)^a$.
\end{e-definition}

@@

By increasing $m$, we increase the number of points of the $(t,m,s)$-net. In the limit case where $m\rightarrow\infty$, we can define the $(t,s)$-sequence as:
\begin{e-definition}%[$(t,s)$-sequence]
For integers $s\geq 1$, $b\geq 2$, and $t\geq 0$, the sequence $\{\vx_i\}_{i\in\mathbb{N}_0}$ is a $(t,s)$-sequence in base $b$, if for every set $\mathcal{P}_{\ell,m}=\{\vx_i\}_{i=\ell b^m}^{(\ell+1)b^m-1}$ with $\ell\geq 0$ and $m\geq t$, $\mathcal{P}_{\ell,m}$ is a $(t,m,s)$-net in base $b$.
\end{e-definition}

@@

Two replicated point sets of order 1, $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$, can be constructed using two $s$-dimensional Sobol' sequences. We note $C_1,\dots,C_s$ the generating matrices used to generate $\mathcal{P}_\ell$ and ${C'}_1,\dots,{C'}_s$ those used to generate $\mathcal{P}'_\ell$. To ensure that $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ are as uniform as possible, these generating matrices need to be different from each other. We choose $C_1,\dots,C_s,{C'}_1,\dots,{C'}_s$ to be the first $2s$ generating matrices suggested by Joe and Kuo in \cite{Kuo}, where they minimized the $t$-value for all $2$ dimensional projections.
\bigskip

>>>>

\begin{e-definition}%[Replicated designs]
\label{rep.designs}
Consider $\vx \in [0,1)^s$, and $\vx_u \in [0,1)^{|u|}$ the subset of elements of $\vx$ given by $u\subsetneq \{1,\dots,s\}$, where $|u|$ is the cardinality of $u$. Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in $[0,1)^{s}$, and denote by $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp. $\mathcal{P}'^u$) the subset of elements of points in $\mathcal{P}$ (resp. $\mathcal{P}'$) indexed by $u$. We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a=1,\dots,s-1$, if for any $u\subsetneq \{1,\dots,s\}$ with $|u|=a$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ are the same point set in $[0,1)^a$, perhaps in a different order.
\end{e-definition}

@@

By increasing $m$, we increase the number of points of the $(t,m,s)$-net. In the limiting case where $m\rightarrow\infty$, we can define the $(t,s)$-sequence as:
\begin{e-definition}%[$(t,s)$-sequence]
For integers $s\geq 1$, $b\geq 2$, and $t\geq 0$, the sequence $\{\vx_i\}_{i\in\mathbb{N}_0}$ is a $(t,s)$-sequence in base $b$, if for every set $\mathcal{P}_{\ell,m}=\{\vx_i\}_{i=\ell b^m}^{(\ell+1)b^m-1}$ with $\ell\geq 0$ and $m\geq t$, $\mathcal{P}_{\ell,m}$ is a $(t,m,s)$-net in base $b$.
\end{e-definition}

@@

Two replicated point sets of order 1, $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$, can be constructed using two $s$-dimensional Sobol' sequences. We note $C_1,\dots,C_s$ the generating matrices used to generate $\mathcal{P}_\ell$ and ${C'}_1,\dots,{C'}_s$ those used to generate $\mathcal{P}'_\ell$. To ensure that $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ are as uniform as possible, these generating matrices need to be different from each other. We choose $C_1,\dots,C_s,{C'}_1,\dots,{C'}_s$ to be the first $2s$ generating matrices suggested by Joe and Kuo in \cite{Kuo}, not necessarily in this order. In \cite{Kuo}, Joe and Kuo minimized the $t$-value for all $2$ dimensional projections.
\bigskip
